---
title: "Assignment 2"
author: "Devanshu Mehrotra"
date: "9/8/2019"
output:
  html_document:
    df_print: paged
Github: https://github.com/DevMeh/607-Assgn-2
---
##### The purpose of this file is to document steps taken for Assignment 2 of Data 607 #####

***Step 1 - Created a local schema called 'Movies' in MYSQL Workbench***

***Step 2 - Created a table called 'ratings' within the 'Movies' schema (see SQL code below)***

_CREATE TABLE ratings_  
    _id INT NOT NULL AUTO_INCREMENT,_    
    _movie_title VARCHAR(255) NOT NULL,_    
    _reviewer_name VARCHAR(255) NOT NULL,_    
    _rating Int NULL,_    
    _PRIMARY KEY (id) );_  
    
***Step 3 - Created a csv file (movies.csv) with the appropriate data and then imported the file using the MYSQL Workbench import function (see screenshots 1-3 for evidence)***

***Step 4 - Set up a connection between Rstudio and MYSQL Database by first installing the RMySql Package which also downloaded the associated DBI package ***

***Step 5 - Created a local connection called 'dbcon' between the Movies database and R studio. Note that due to manage connection errors due to updated encryption protocols, I had to create a new user(devin) with "Standard" encryption and give this user admin rights *** 

```{r}
dbcon <-  dbConnect(RMySQL::MySQL(), 
                  dbname = 'Movies', 
                  host = '127.0.0.1', 
                  port = 3306,
                  user ='devin',
                  password ='') 
```
                    
***Step 6 - In order to query the database and create an instance of the data within MYSQL used dbSendQuery***

```{r}
rs = dbSendQuery(dbcon, "select * from ratings")
```

***Step 7 - To create a dataframe, fetched the query result and passed it into a new dataframe called df***

```{r}
df = fetch(rs, n=-1)
```

***Step 8 - View the resulting dataframe***

```{r}
df
```
    
